Replicate earlier study

### 2023-04-01 x_replicate.qmd
getting data prep in place

# runway 
source("~/RProjects/paper-2023-ICNS/R/cast_sf_rwy.R")
```

@@

  phase <- ds |> 
    extract_4d_nest() |> 
    confirm_arrival_at(apt_box) |> 
    check_arrival_orphan()
}
```

@@

part of data cleaning 
- remove stray orphans inside aerodrome

gotcha |> ungroup() |> filter(ARR) |> mutate(GOTCHA = RWY_TRUST >= quantile(RWY_TRUST, probs = 0.1)) |> filter(GOTCHA, N_LAST < 15) |> filter(UID == "3c66b1-1") |> unnest(last_4d) |> ggplot() + geom_point(aes(x = LON, y = LAT)) + geom_point(data = arp, aes(x = LON, y = LAT), color = "red", size = 3) + geom_sf(data = my_apt_box, fill = NA)

rq |> 
  # subset for ICAO24s seen at the study airport
  filter(ICAO24 %in% seen_at_airport$ICAO24) |> 
  spatial_subset_jormungand(jormungand) |> 
  # human readable TIME
  coerce_unixepoch_to_datetime() |>
  # clean ALT and trim for airborne part with heuristic fix
  Alt_Outlier_filter(.alt_var = ALT_B) |> 
  fix_altitude_heuristic() |> 
  # assign leg for each airborne segment
  identify_trajectory_legs() |> 
  # force single FLTID here to construct niche UIDs
  group_by(ICAO24, LEG) |> fix_invalid_fltid() |> ungroup() |> 
  # construct UID
  mutate(UID = paste(ICAO24, LEG, sep = "-"))

>>>>

# runway 
source("~/RProjects/paper-2023-ICNS/R/cast_sf_rwy.R")

source("~/RProjects/paper-2023-ICNS/R/assign_threshold_time2.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_bearing_to_target.R")
source("~/RProjects/paper-2023-ICNS/R/estimate_threshold_time.R")
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_landing_time_to_nested_data.R")
```

@@

  phase <- ds |> 
    extract_4d_nest() |> 
    confirm_arrival_at(apt_box) |> 
    check_arrival_orphan()

  # # add landing time
  # with_ldg_time <-  phase |> 
  #   dplyr::mutate(
  #     study_trj = 
  #     case_when(
  #       ARR & ! ORPHAN ~ pmap(
  #             .l = list(data, UID, RWY)
  #           , .f = ~ add_landing_time_to_nested_data(..1, ..2, ..3, rwys))) 
  #     , TRUE ~ "Departure"
  #   )
}
```

@@

```{r}
test_landing_time <- function(phase, rwys = rwys_egll){

  arrs <- phase |> filter(ARR & !ORPHAN)
  rest <- phase |> filter(! UID %in% arrs$UID )

  with_ldg_time <-  arrs |>
    dplyr::mutate(
      study_trj = pmap(
              .l = list(data, UID, RWY)
            , .f = ~ add_landing_time_to_nested_data(..1, ..2, ..3, rwys)
            )
      ) |> 
   # dplyr::mutate(study_trj = map(.x = study_trj, .f = ~ interpolate_lin_4D(.x, .source = "OSN"))) |> 
    dplyr::mutate(ALDT = map(.x = study_trj, .f = ~ filter(.x, MST == "ALDT") |> pull(TIME))) |> tidyr::unnest(ALDT)

  return(bind_rows(with_ldg_time, rest))
}

(
  mickey <- gotcha |> test_landing_time()
)
```

```{r}
study_sequences <- mickey |> filter(ARR, !ORPHAN) |> select(UID, RWY, ALDT) |> 
  arrange(RWY, ALDT, UID) |> 
  group_by(RWY) |> 
  mutate(LEAD_DELTA = difftime(ALDT, lag(ALDT, default = first(ALDT)), units = "sec"))
study_sequences
```
